### 2010-07-07 code/subarchitectures/visualization.sa/trunk/doc/v11n.tex
v11n: minor doc update

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   class VideoViewer : public ManagedComponent, public VideoClient
   {
   private:
   #ifdef FEAT_VISUALIZATION
     cogx::display::CDisplayClient m_display;
   #endif
   };
\end{Verbatim}

@@

An active display client is needed when the component wants to present some UI
elements with which it can be configured. The client receives notifications and
requests related to these elements from the display server. The component must
define two callback functions that will handle the events sent by the server.

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   class VideoViewer : public ManagedComponent, public VideoClient
   {
   private:
   #ifdef FEAT_VISUALIZATION
     cogx::display::CActiveDisplayClient<VideoViewer> m_display;
     void handleGuiEvent(const Visualization::TEvent &event);
     std::string getControlState(const std::string& ctrlId);
   #endif
   };
\end{Verbatim}

The event path from the server to the client must be initiated. This is done right
after the component connects to the client. After the connections are established,
the callback functions are registered:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   void VideoViewer::start()
   {
   #ifdef FEAT_VISUALIZATION
     m_display.connectIceClient(*this);
     m_display.installEventReceiver();
     m_display.setEventCallback(this, &VideoViewer::handleGuiEvent);
     m_display.setStateQueryCallback(this, &VideoViewer::getControlState);
   #endif
   }
\end{Verbatim}

>>>>

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   #ifdef FEAT_VISUALIZATION
   #include <CDisplayClient.hpp>
   #endif
   ...
   class VideoViewer : public ManagedComponent, public VideoClient
   {
   private:
   #ifdef FEAT_VISUALIZATION
     cogx::display::CDisplayClient m_display;
   #endif
   };
\end{Verbatim}

@@

An active display client is needed when the component wants to present some UI
elements with which it can be configured. The client receives notifications and
requests related to these elements from the display server. To achieve this 
a few methods must be overridden in a class derived from the CDisplayClient:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   class VideoViewer : public ManagedComponent, public VideoClient
   {
   private:
   #ifdef FEAT_VISUALIZATION
     class CVvDisplayClient: public cogx::display::CDisplayClient
     {
       VideoViewer* pViewer;
     public:
       CVvDisplayClient() { pViewer = NULL; }
       void setClientData(VideoViewer* pVideoViewer) { pViewer = pVideoViewer; }
       void handleEvent(const Visualization::TEvent &event); /*override*/
       std::string getControlState(const std::string& ctrlId); /*override*/
     };
     CVvDisplayClient m_display;
   #endif
   };
\end{Verbatim}

In the constructor of the VideoViewer we call \code{setClientData()} so that
the new display client will be able to access the VideoViewer:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
  VideoViewer() : camId(0)
  {
#ifdef FEAT_VISUALIZATION
    m_display.setClientData(this);
#endif
  }
\end{Verbatim}

The event path from the server to the client must be initialized. This is done
right after the component connects to the client:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   void VideoViewer::start()
   {
   #ifdef FEAT_VISUALIZATION
     m_display.connectIceClient(*this);
     m_display.installEventReceiver();
   #endif
   }
\end{Verbatim}
